---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ModelList

<!-- badges: start -->
<!-- badges: end -->

The goal of ModelList is to create an S3 class ModelList which is a container of regression or other models. There are methods for summary and predict that can be used on this class. This was created for HW3 in PH290 at UCB.

## Installation

You can install this version of ModelList from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("madelineadee/PH290-ModelList")
```

## Example

This is a basic example which shows you how to use the package:

Setup and run models. 

```{r example}
library(ModelList)

# create two sets of data
df <- mtcars
sample <- sample(c(TRUE, FALSE), nrow(df), replace=TRUE, prob=c(0.5,0.5))
train  <- df[sample, ]
test   <- df[!sample, ]

mod1 <- lm(mpg ~ cyl, train)
mod2 <- lm(mpg ~ cyl + am, train)

```

Create the ModelList container of models.

```{r}

mList <- CreateModelList(mod1, mod2)


```

Summary method for ModelList class.

```{r}

summary(mList)

```

Predict method for ModelList class.

```{r}

predict(mList, test)

```

